I can see clearly now: reinterpreting statistical significance

### 2018-05-25 doc.tex

\textbf{Signs}.
Who has said before that we test zero \emph{because} we want to know if we can see a sign clearly? If nobody, how much time do we want to spend on that point?

>>>>

\textbf{Signs}.
Who has said before that we test zero \emph{because} we want to know if we can see a sign clearly? If nobody, how much time do we want to spend on that point? 
From \citet{robinson2001past}, which arose from \citet{jones2000sensible}: [instead of no difference, or no statistical difference] "authors should instead simply state that `the direction of the differences among the treatments was undetermined' or that `the sign of the correlation among the two variables was undetermined.'" --- That is, "If p is greater than 0.05, the conclusion is simply that the sign of the difference is not yet determined"
